### 2012-05-21 docs/makefiles/makefiles.tex
still more...

@@

dependency generation

include files

>>>>

The \maestro\ executable is built from source distributed across a
number of directories.  In each of these directories containing source
files, there is a {\tt GPackage.mak} file.  This file has a number of
lines of the form:
\begin{verbatim}
f90sources += file.f90
\end{verbatim}
where {\tt file.f90} is a source file that should be built when this
directory is added to the list of build directories.  For old
fixed-form Fortran files, the files should be added to the {\tt
fsources} variable instead of {\tt f90sources}.

@@

There is no need to explicitly define the dependencies between the
source files for Fortran modules.  The scripts in {\tt
BOXLIB\_HOME/Tools/F\_scripts/} are run at the start of the build
process and parse all the source files and make an explicit list of
the dependency pairs.  This process is defined in {\tt
GMakerules.mak}.

A few files use explicit `{\tt include}' statements to include Fortran
source in other source files.  Any include file locations should be
added to {\tt Fmincludes} variable in the problem's {\tt GNUmakefile}.
This does not occur frequently.  For the case of the {\tt helmeos}
equation of state, this is done automatically in {\tt GMaestro.mak}.
